He-Man: A domain-specific language for lightweight concurrency

### 2011-12-12 report/report.tex
Related work.

The Lighttpd \cite{Lighttpd} and Nginx \cite{Nginx} HTTP servers use event-based
architectures, with the stated goal of addressing the C10k problem. Indeed, they
are fast (XXX CITATION)

@@

@@

and I/O time (both network and disk) probably dominates computation time

>>>>

The C10K problem is particularly evident in the context of HTTP servers, which
routinely maintain many concurrent connections. The popular Lighttpd and Nginx
HTTP server projects were both started with the explicit goal of addressing the
C10K problem \cite{Lighttpd,Nginx}, and both use event-based architectures
similar to He-Man.

A number of functional languages support lightweight threads with user-space
scheduling, most notably Erlang, which was designed for highly concurrent
telecommunications applications, and easily scales to 20,000 clients
\cite{Hellstrom}. Haskell

@@

FoxNet: \cite{BiagioniEtAl}

@@

I/O time (both network and disk) dominates the computation time
